---
title: "Text Cleaning Documentation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr);library(ggplot2);library(data.table);library(tidyr);library(stringr)
library(tidytext);library(textstem);library(SnowballC);library(naniar);library(textclean)

```

```{r include=FALSE, echo=FALSE}
##### 1. READ DATA FROM DATABASE #############
# library("RPostgreSQL")
# # connect to postgresql to get data (in rivanna)
# conn <- dbConnect(drv = PostgreSQL(),
#                   dbname = "sdad",
#                   host = "10.250.124.195",
#                   port = 5432,
#                   user = Sys.getenv("db_userid"),
#                   password = Sys.getenv("db_pwd"))
# # query the bipartite edgelist data from github data
# data0 <- dbGetQuery(conn, "SELECT * FROM american_soldier.survey_32_combined")
# data_clean <- dbGetQuery(conn, "SELECT * FROM american_soldier.survey_32_clean")
# dbDisconnect(conn)
# data <- data0 %>% unite(long, long_comment:long_comment_cont, sep = " ", na.rm = TRUE) %>% # first unite the long response and it's continued text 
#   mutate(long = tolower(long), outfits_comment = tolower(outfits_comment),  # make entire text lowercase 
#          index= 1:nrow(data0)) # add an index column
```

### 1. Data is read in from the database.
The columns outfits_comment, long_comment and long_comment_cont, contain the transcribed responses of soldiers from S32N and S32W. The outfits_comment corresponds to question 62a in S32W and 77a in S32N which asks whether black and white soldiers should be in separate outfits. Long_comment_cont is a continuation of long_comment which asked soldiers about their overall thoughts on the questionnaire.


### 2. Data undergoes initial processing.
The following alterations are made to the data in order to prep for text cleaning:   

* long_comment and long_comment_cont are combined into a single column called long.    
* all text are converted to lowercase   
* index column is added   


### 3. Meaningless responses converted to NA

In both the outfit and long responses, there exists responses that indicate an lack of input such as  "none", "n/a" or 0. These instances are converted to NA for easy filtering when performing analysis.    


### 4. Automated metatag removal
Metatags are included in the transcriptions by the zooniverse transcribers to indicate attributes or corrections to the text. Further documentation on these metatags can be found in the file *metatag_documentation*.
The following metatags are completely removed from responses:    
* underline: [underline] and [/underline]  
* circle: [circle] and [/circle]      
* insertion: [insertion] and [/insertion]    
* deletion: [deletion]text[/deletion]. The tags themselves as well as the text in between are removed from the response.  
* unclear without words: [unclear][/unclear] and [unclear]???[/unclear]



### 5. Unclear metatag cleaning   

The following steps are taken to manually clean the unclear metatags:  

1.	Table of all instances of unclear cases are created for both the long and outfit questions. The columns are:  
        +	Long or Outfits_Comment: Transcribed response of the soldier  
        + Racial_group: categorical variable indicating black or white soldier  
        + Index: The row of the transcribed response in the original dataset.  
        + Unclear: The instance of use for the unclear tag that needs to be corrected.  
        + Correct: correction to the unclear entity  
      
2.	A table of the unclear cases is stored in the data folder under the name “long_unclear.csv” or “outfits_unclear.csv”

3.	Researcher manually enters correction for unclear word on their local text editor then re-uploads most updated file in the repo under the same name. Researcher should refer to the transcribed response to make judgement on the best correction for the unclear word.        
        +	 If there is no logical correction, leave the correction field for that unclear word blank.     
        +  If the word inside the unclear tags is already correct, just re-type the word in the correction column.   
4.	The R script loops through the .csv file and updates the corrections to the clean dataset.     

Steps 1-3 of the unclear metatag cleaning are included in the cleaning script but are commented out.   


### 6. Bracketed text cleaning
Like unclear metatags, bracketed text is manually cleaned by the researcher. The steps are detailed below: 

1.	Table of all instances of unclear cases are created for both the long and outfit questions. The columns are:  
        +	 Long or Outfits_Comment: Transcribed response of the soldier   
        +  Racial_group: categorical variable indicating black or white soldier   
        +  Index: The row of the transcribed response in the original dataset.   
        +  Bracket: The instance of use for the unclear tag that needs to be corrected.   
        +	 Correct: Full text of the corrected response.   
2.	A table of the unclear cases is stored in the data folder under the name “long_bracket.csv” or “outfits_bracket.csv” 

3.	Researcher manually corrects the response on their local text editor then re-uploads most updated file in the repo as "long_bracket_corrected.csv" or "outfits_bracket_corrected.csv".

4.	The R script loops through the .csv file and updates the corrections to the clean dataset.     

Steps 1-3 of the unclear metatag cleaning are included in the cleaning script but are commented out.  

### 7. Manual Spell-Checking   

1. The hunspell spell-checking package is applied to unique tokenized words from both the outfits and long response to identify mispelled words and provide spelling suggestions. 

2. A dataframe of the mispelled unique words that occur more than 2 times throughout the entire body of text and their primary spelling suggestion from the hunspell package are exported to a file named "spell_check.csv". 

3. The researcher then manually checks and corrects the spelling suggestions as well as adding their own detected mispellings. 

4. Finally, the R script corrects all spellings in the "spell_check.csv" file.

Steps 1-3 of the unclear metatag cleaning are included in the cleaning script but are commented out.  


### 8. Final Processing
* contractions are replaced: don't --> do not
* responses that contain an empty string are replaced with NA

### 9. Push clean data to database.
