---
title: "Gender Analysis"
author: "Mary Solomon"
date: "7/19/2020"
output: html_document
---


In addition to analyzing race relations between soldiers, we want to see how gender roles were discussed amongst soldiers. Our particular focus is on women, but both male and female roles are explored.


### Preparing the data
```{r setup, include=FALSE}
#libraries
library(tidytext)
library(data.table)
library("RPostgreSQL")
library(stringi)
library(textstem)
library(dplyr)
library(tidyr)
library(SnowballC)
library(igraph)
library(ggraph)
library(widyr)
library(stringr)
```

```{r functions}
# Visualizing Bigrams functions
# From tidytext documentation
visualize_bigrams <- function(bigrams, title) {
  set.seed(2020)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void() + theme(legend.position = "none",
                      plot.title = element_text(hjust = 0.5)) +
    ggtitle(title)
}

cooccur_gender <- function(data, dictionary, n=5, corr=.15){
  
  data %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= n) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(dictionary, item1))%>%
  filter(correlation >= corr) 
}
visualize_cooccur <- function(data, title){
  set.seed(2020)
  data %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle(title)
}

```

```{r dataload}
conn <- dbConnect(drv = PostgreSQL(),
                  dbname = "sdad",
                  host = "10.250.124.195",
                  port = 5432,
                  user = Sys.getenv("db_userid"),
                  password = Sys.getenv("db_pwd"))
# query the bipartite edgelist data from github data
data <- dbGetQuery(conn, "SELECT * FROM american_soldier.survey_32_clean")
dbDisconnect(conn)

##### some data cleaning
#remove possessive 's
data$outfits_comment <- str_replace_all(data$outfits_comment, "'s", "")
data$long <- str_replace_all(data$long, "'s", "")

data$outfits_comment <- str_replace_all(data$outfits_comment, "\\+", "and")
data$long <- str_replace_all(data$long, "\\+", "and")

#remove all symbols except periods.
data$outfits_comment <- str_replace_all(data$outfits_comment, "[^[:alnum:][:space:].]", "")
data$long <- str_replace_all(data$long, "[^[:alnum:][:space:].]", "")


#### create custom stop words 
custom_stop <- append(stop_words$word, c("question", "questionnaire", "answer"))
```


# How do Black and White soldiers talk about gender roles?

The following analysis will explore which words are paired and associated with female and male words.

A dictionary of gender words are loaded to identy which responses relate to gender topics. 
```{r dictionaryload}
#load dictionary csv
gender_words <- fread("~/git/dspg2020amsoldier/data/dictionary/gender.csv", sep = ",");head(gender_words) 
gender_match <- paste(paste("\\b", gender_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
```

```{r data_subset}
#subset data based on question and race
S32W_short <- data %>% filter(racial_group== "white") %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32W_short <- tibble(nrow=1:nrow(S32W_short), text = S32W_short$outfits_comment)

S32W_long <- data %>% filter(racial_group== "white") %>% select(long) %>% filter(!is.na(long))
S32W_long <- tibble(nrow=1:nrow(S32W_long), text = S32W_long$long)

S32N_long <- data %>% filter(racial_group== "black") %>% select(long) %>% filter(!is.na(long))
S32N_long <- tibble(nrow=1:nrow(S32N_long), text = S32N_long$long)

```


###Bi-Grams
To view commentary on gender relations, we will look at the bi-grams which will show which words appear next to gender related words.

```{r bigram_create}
#### unnest tokens into bigrams
#### counts bigrams, but filter for those that have words in the gender dictionary.
#### separates bigrams into word1 and word 2 column
#### removes rows that contain a stopword
#### lem then stem words
#### finally count the bigrams.
short_bigrams_gender <- S32W_short %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>% 
  count(word1, word2, sort = TRUE)

longW_bigrams_gender <- S32W_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>% 
  count(word1, word2, sort = TRUE)

longN_bigrams_gender <- S32N_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE)
```


```{r bigram_visualize, include = FALSE}
visualize_bigrams(short_bigrams_gender, "White Soldiers' Outfits Response - Gender Words")
visualize_bigrams(longW_bigrams_gender, "White Soldiers' Long Response - Gender Words")
visualize_bigrams(longN_bigrams_gender, "Black Soldiers' Long Response - Gender Words")
```


In the white soldiers' responses on the outfits separation question, we can see that the associations to gendered words are primarily related to racial identity. Since we are interested in investigating how conversations about gender differed between the two racial groups, we will join the two words into one. For example, color boi will be collapsed to colorboi, to see which words are used with this subject.
 
Overall, there's a wider variety of words that the black soldiers are using in their long responses.



```{r include = FALSE, echo = FALSE}
#co-occurances
section_words <- S32N_long %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word)
word_cors <- section_words %>%
  group_by(word) %>% 
  filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(gender_match, item1))

#plot
word_cors %>%
  filter(correlation > .15) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle("Black Soldiers' Long Response - Gender Related Co-occurences")
```



### Bi-Grams: Words-collapsed

With bi-grams, we will explore which words are paired with gender related words. 
```{r}
#load dictionary csv
gender_words <- fread("~/git/dspg2020amsoldier/data/dictionary/gender.csv", sep = ",") 
gender_match <- paste(paste("\\b", gender_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 

####collapse certain two word phrases like white man --> whiteman

#read the csv file of correct spellings back in.
collapse <- fread("~/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",") 
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) #so that stringr doesn't pick up on instances where it is part of another word

#replace with collapsed words
data$long <- stri_replace_all_regex(data$long, collapse$original, collapse$collapse, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, collapse$collapse, vectorize_all = FALSE)
```


```{r }
#subset data based on question and race
S32W_short2 <- data %>% filter(racial_group== "white") %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32W_short2 <- tibble(nrow=1:nrow(S32W_short2), text = S32W_short2$outfits_comment)

S32W_long2 <- data %>% filter(racial_group== "white") %>% select(long) %>% filter(!is.na(long))
S32W_long2 <- tibble(nrow=1:nrow(S32W_long2), text = S32W_long2$long)

S32N_long2 <- data %>% filter(racial_group== "black") %>% select(long) %>% filter(!is.na(long))
S32N_long2 <- tibble(nrow=1:nrow(S32N_long2), text = S32N_long2$long)
```

```{r }
#### unnest tokens into bigrams
#### counts bigrams, but filter for those that have words in the gender dictionary.
#### separates bigrams into word1 and word 2 column
#### removes rows that contain a stopword
#### lem then stem words
#### finally count the bigrams.
short_bigrams_gender2 <- S32W_short2 %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE)

longW_bigrams_gender2 <- S32W_long2 %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE)

longN_bigrams_gender2 <- S32N_long2 %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(gender_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
```

```{r }
visualize_bigrams(short_bigrams_gender2, "White Soldiers' Outfits Response - Gender Words")
```

White soldiers short response: 

* only comments about either black or white men are mentioned. This is logical since the question asks soldiers about whether black and white soldiers should be in separate outfits or not. 


```{r }
visualize_bigrams(longW_bigrams_gender2, "White Soldiers' Long Response - Gender Words")
```


White soldiers long response: 

* rarely talk about black men or women. one presence of "colorman" that does exist is paired with despise.   

* We also see that white soldiers are talking about interracial marriage.   

* White commentar on the word woman are paired with wrods relating to women in the workforce such as worker, and waac and auxiliari which refer to the Women's Army Corps.    




```{r }
visualize_bigrams(longN_bigrams_gender2, "Black Soldiers' Long Response - Gender Words")
```

Black soldier long response: 

* A commonality between the black and white soldier commentary regarding females, is that their role as wife or mother is prevelant.  

* When talking about gender(both male and female) there is more commentary specifying racial groups as opposed to how white soldiers are talking about gender in their long responses. A notable bi-gram is the series of words following the node of whitewoman: whitewoman->holler->rape. In addition, when the white men are talked about, they are most frequently paired with the adjective southern. This is relating to commentary of how southern white men treated black men at the time.

* colorwoman used with the words whip and vice    



In all of the responses, the prevelance of familial words such as mother, father, brother, sister shows that soldiers frequently discussed family.



### Co-Occurrences

With co-occurrences we want to measure the proximity of words that occur with gender related words. The co-ooccurring words do not have to be directly before or after the gender word of interest.   
The co-occurances are measured with pearson's coefficient to measure the correlation of occurances between words. 

The threshold for the long responses are words that occur more than 5 times and correlations greater than .15. 
The threshold for the short responses is lower than that of long because it is a smaller body of text with correlations greater than .10

```{r}
gender_match <- stem_words(lemmatize_words(gender_match))
```


#### white soldiers short response
```{r}
S32W_short_cors <- S32W_short2 %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(gender_match, item1))%>%
  filter(correlation > .10) 

#plot
S32W_short_cors  %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle("White Soldiers' Short Response - Gender Related Co-occurences")
```

Only a small handful of the outfits questions mention a word relating to the female gender. Due to the settings filtering for words that occur more than 5 times in the data, these occurrances don't show.

An interesting observation is that colored men are correlated with the word jealousy and whiteman correlated with the word clean.This provides further insight to the sentiment that white soldiers had towards themselves versus black soldiers. Furthermore, the strong correlation between whiteman and negro implies that the relationship between the two were talked about often.  

no threshold for word count to show co-occurances that mention female relating words. 
```{r}
S32W_short_cors <- S32W_short2 %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  #filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(gender_match, item1))%>%
  filter(correlation > .10) 

#plot
S32W_short_cors  %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle("White Soldiers' Short Response - Gender Related Co-occurences")
```

It shows that wife has a great number of correlates, however, there is only one comment that mentions wife, and therefore, is not representative of the overall discussion of wives in relation to the question.   

```{r}
data$outfits_comment[5726]
```

Upon closer inspection, this comment seems to be an error in data storage and is more related to the long response question.


#### white soldiers long response
```{r}
S32W_long_cors <- S32W_long2 %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(gender_match, item1))%>%
  filter(correlation > .15) 

#plot
S32W_long_cors  %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle("White Soldiers' Long Response - Gender Related Co-occurences")
```


#### Black soldiers long response
```{r}
S32N_long_cors <- S32N_long2 %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(gender_match, item1))%>%
  filter(correlation >= .15) 

#plot
S32N_long_cors  %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle("Black Soldiers' Long Response - Gender Related Co-occurences")


### try networkD3
# colnames(S32N_long_cors) <- c("Source", "Target", "Weight")
# S32N_long_cors <- filter(S32N_long_cors, correlation > .20)
# simpleNetwork(S32N_long_cors)
```

When talking about whitemen specifically, the correlated words show that the soldiers will talk about relations to black men and fighting. When talking about women there is a distinction made between white and black women. Other than those cluster of words, women are often talked about as family members and home life.


# FEMALE WORDS ONLY
```{r}
#split the dictionary so we can analyze male and female separately
female_words <- gender_words %>% filter(category == "female") 
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 

male_words <- gender_words %>% filter(category == "male") 
male_match <- paste(paste("\\b", male_words$gender,"\\b", sep = ""), collapse="|") #regex friendly

collapse <- fread("~/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",") 
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) #so that stringr doesn't pick up on instances where it is part of another word

#make sure replace with collapsed words
data$long <- stri_replace_all_regex(data$long, collapse$original, collapse$collapse, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, collapse$collapse, vectorize_all = FALSE)
```


### long-All soldiers
```{r}
S32_long <- data %>% select(long) %>% filter(!is.na(long))
S32_long <- tibble(nrow=1:nrow(S32_long), text = S32_long$long)

long_bigrams_female <- S32_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE)

visualize_bigrams(long_bigrams_female, "Soldiers' Long Response - Female Words Bigrams")
```

The most frequent pairs of words being used when talking about the female gender is familial roles such as wife and relations to family like dad.

colorwoman -> whip
```{r}
filter(S32_long,nrow == 690)$text
```

negrowoman -> graduat & negrowoman -> attain
```{r}
filter(S32_long,nrow == 3356)$text
```

This response shows that despite the segregation of black and white Americans, there were some opportunities available to Black women at the time. The following link explains the acceptance of Black women into the army training school in Des Moines, Iowa: http://www.iowapbs.org/iowapathways/mypath/female-black-officers-train-des-moines-world-war-ii





Try above analysis again but with dictionary including relationship words
```{r}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32_long <- data %>% select(long) %>% filter(!is.na(long))
S32_long <- tibble(nrow=1:nrow(S32_long), text = S32_long$long)

long_bigrams_female <- S32_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "Soldiers' Long Response - Female Words Bigrams")
```

Now, when including like as a relationship word, we can see at the like node there is a chain of "whiteman like colorwoman." There are also instances of whiteman are like black men/soldiers. This is either relating the two in similarity or in emotion of likeness between the two.

Another interesting addition to the network with relationship words is the chain of bigrams "sex intercourse with whitewoman". A hot topic was white soldiers being concerned with black soldiers having sexual relations with 'their' whitewomen. Likewise, black soldiers were aware of the tension of being falsely accused for raping or having sex with white women.

Otherwise, themes of family are prevelant for women's role in the commentary of the soldiers. We can also see the different pairings with the word woman, seeming to talk about their roles as workers amongst other attributes  (worker, waac, auxiliary)

In similarity with the previous versions of the bigram networks, th



create coocurrance of same data
```{r}
long_fem_co <- cooccur_gender(S32_long, female_match, n=5, corr=.12)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long soldier response")
```

Themes of family are still prevelant. Negrowoman are associated with some negative words like filthy and invade. Whitewomen associations with the words intercourse, cry and molest are related to the controversy of black men having sexual realtions with whitemen. In addition, whitewomen is associated with negroman. This is shows that there is commentary of the association of black and white women which was controversial at the time. 


### long - Black
```{r}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32N_long <- data %>% select(racial_group,long) %>% filter(!is.na(long), racial_group == "black")
S32N_long <- tibble(nrow=1:nrow(S32N_long), text = S32N_long$long)

long_bigrams_female <- S32N_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "Black Soldiers' Long Response - Female Words Bigrams")
```




create coocurrance of same data
```{r}
long_fem_co <- cooccur_gender(S32N_long, female_match, n=5, corr=.12)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long Black soldiers' responses")
```

One of the strongest correlations are between negrowoman and negroman as well as negroman and whitewoman. This is indicative that interracial relations are one the most heavily correlated topics to women in the Black soldiers' responses. 
In addition, mother, sister and father have some of the strongest correlations, showing that women's most prevalent role for the soldiers was in their families.  

### long - White

```{r}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32W_long <- data %>% select(racial_group,long) %>% filter(!is.na(long), racial_group == "white")
S32W_long <- tibble(nrow=1:nrow(S32W_long), text = S32W_long$long)

long_bigrams_female <- S32W_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "White Soldiers' Long Response - Female Words Bigrams")
```

We see a complete lack of narrative in black women specifically. Conversations about women are mostly about their role in the family as a mother, wife or sister. Another common conversation is about working women, with pairings to WAAC, auxiliary (referring to WAAC) and worker.


```{r}
long_fem_co <- cooccur_gender(S32W_long, female_match, n=5, corr=.15)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long White soldiers' responses")
```



### short - All soldiers
```{r}
female_words <- gender_words %>% add_row(gender = "like", category = "relation")#%>% filter(category == "female" | category == "relation") 
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32_short <- data %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32_short <- tibble(nrow=1:nrow(S32_short), text = S32_short$outfits_comment)

short_bigrams_female <- S32_short %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
short_bigrams_female <- short_bigrams_female[!(short_bigrams_female$word1 == "like" & !short_bigrams_female$word2 %in% keep_female),]
short_bigrams_female <- short_bigrams_female[!(short_bigrams_female$word2 == "like" & !short_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(short_bigrams_female, "Soldiers' Short Response - Female Words Bigrams")
```


```{r}
short_fem_co <- cooccur_gender(S32_short, female_match, n=5, corr=.12)
short_fem_co <- short_fem_co[!(short_fem_co$item1 == "like" & !short_fem_co$item2 %in% keep_female),]
short_fem_co <- short_fem_co[!(short_fem_co$item2 == "like" & !short_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for short soldier response")
```


# EXTRA material

Interesting commentary from a black soldier on race relations
```{r}
data$long[346]
```