---
title: "Male Perspectives on WAC's - Survey 195"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggthemes)
```

# Introduction

In addition to race relations in the Army, we are also focused on perspectives on women and gender within the military. The questions and responses are mostly geared towards WACs, which are Women's Army Corps members. In addition to survey 32, which captures textual data on gender in teh Army, a survey was given out in January of 1945 to capture perspectives of male soldiers on their WAC counterparts. This survey is survey 195B. From survey 32's textual data we have extracted insights into what topics and words male soldiers used to discuss women, and from survey 195 we have been able to identify general persepectives of soldiers on WACs.

# Exploratory Data Analysis

Survey 195 has 11 larger questions about WACs in which soldiers are asked a yes/no/no answer question which is then followed by a question of how strongly they feel on a very/fairly/not/no answer scale. From this, we can extract that most soldiers felt negatively towards WACs and of those that felt negatively, they also felt very strongly about their answers.

```{r eda, echo=FALSE}

s195b <- read.csv("~/git/dspg2020amsoldier/data/working/AMS195B_answers.csv")
s195c <- read.csv("~/git/dspg2020amsoldier/data/working/AMS195C_answers.csv")
s35 <- read.csv("~/git/dspg2020amsoldier/data/working/AMS0035_answers.csv")

colors <- c("#232d4b",
            # "#2c4f6b",
            "#0e879c","#60999a","#d1e0bf","#d9e12b","#e6ce3a","#e6a01d","#e57200","#fdfdfd")

my_cols = c("232d4b","2c4f6b","0e879c","60999a", "9bc0c0","d1e0bf", "ebf094", "d9e12b","e6ce3a","e6a01d","e57200","a35200","fdfdfd")
my_cols = paste0('#', my_cols)

s195b$Q.14A. <- recode_factor(s195b$Q.14A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.14B. <- recode_factor(s195b$Q.14B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

# s195b %>%
#   group_by(Q.14A., Q.14B.) %>%
#   count() %>%
#   ggplot(aes(x = Q.14A., y = n)) +
#   geom_bar(stat="identity", aes(fill = Q.14A.)) +
#   ggtitle("IN YOUR OPINION IS IT NECESSARY FOR THE \nWAR EFFORT TO HAVE WOMEN IN THE ARMY?") +
#   facet_wrap(~Q.14B.) +
#   ylab("Number of Responses") +
#   xlab("Responses") +
#   theme_minimal() +
#   scale_fill_manual(values = colors)

s195b %>%
  ggplot(aes(x=Q.14A.)) +
  geom_bar(position = "dodge", fill = 'darkslategray4') +
  labs(title="IN YOUR OPINION IS IT NECESSARY FOR THE \nWAR EFFORT TO HAVE WOMEN IN THE ARMY?", x="Answers", y = "Count")

s195b %>%
  ggplot( aes(x=Q.14A., fill = Q.14B.)) +geom_bar(position= "fill") +
  labs(title="IN YOUR OPINION IS IT NECESSARY FOR THE \nWAR EFFORT TO HAVE WOMEN IN THE ARMY?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q15A. SUPPOSE A GIRL FRIEND OF YOURS WAS CONSIDERING JOINING THE WAC, WOULD YOU ADVISE HER TO JOIN OR NOT TO JOIN? 1. YES 2. NO 0. NO ANSWER
s195b$Q.15A. <- recode_factor(s195b$Q.15A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.15B. <- recode_factor(s195b$Q.15B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot(aes(x=Q.15A.)) +
  geom_bar(position = "dodge", fill = 'darkslategray4') +
  labs(title="SUPPOSE A GIRL FRIEND OF YOURS WAS CONSIDERING JOINING THE\nWAC, WOULD YOU ADVISE HER TO JOIN OR NOT TO JOIN?", x="Answers", y = "Count")

s195b %>%
  ggplot( aes(x=Q.15A., fill = Q.15B.)) +geom_bar(position= "fill") +
  labs(title="SUPPOSE A GIRL FRIEND OF YOURS WAS CONSIDERING JOINING THE\nWAC, WOULD YOU ADVISE HER TO JOIN OR NOT TO JOIN?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q16A. IN YOUR OPINION ARE THE JOBS WHICH WOMEN IN THE WAC DO LESS IMPORTANT THAN THE JOBS WHICH ARE DONE BY MEN IN THE ARMY WHO ARE NOT ON COMBAT DUTY? 1. YES 2. NO 0. NO ANSWER
s195b$Q.16A. <- recode_factor(s195b$Q.16A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.16B. <- recode_factor(s195b$Q.16B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.16A., fill = Q.16B.)) +geom_bar(position= "fill") +
  labs(title="IN YOUR OPINION ARE THE JOBS WHICH WOMEN IN THE WAC DO LESS IMPORTANT \nTHAN THE JOBS WHICH ARE DONE BY MEN IN THE ARMY WHO ARE NOT ON COMBAT DUTY? ", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q17A. IF YOU HAD A SISTER, 21 YEARS OR OLDER, WOULD YOU LIKE TO SEE HER JOIN THE WAC OR NOT? 1. YES 2. NO 0. NO ANSWER
s195b$Q.17A. <- recode_factor(s195b$Q.17A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.17B. <- recode_factor(s195b$Q.17B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.17A., fill = Q.17B.)) +geom_bar(position= "fill") +
  labs(title="IF YOU HAD A SISTER, 21 YEARS OR OLDER, WOULD YOU LIKE TO SEE HER JOIN THE WAC OR NOT?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q18A. CAN A WOMAN DO MORE FOR HER COUNTRY IN THE WAC THAN SHE CAN BY WORKING IN A WAR INDUSTRY? 1. YES 2. NO 0. NO ANSWER
s195b$Q.18A. <- recode_factor(s195b$Q.18A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.18B. <- recode_factor(s195b$Q.18B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.18A., fill = Q.18B.)) +geom_bar(position= "fill") +
  labs(title="CAN A WOMAN DO MORE FOR HER COUNTRY IN THE WAC THAN SHE CAN BY WORKING IN A WAR INDUSTRY?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q19A. WILL THE TRAINING A WOMAN GETS IN THE WAC BE USEFUL IN CIVILIAN LIFE? 1. YES 2. NO 0. NO ANSWER
s195b$Q.19A. <- recode_factor(s195b$Q.19A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.19B. <- recode_factor(s195b$Q.19B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.19A., fill = Q.19B.)) +geom_bar(position= "fill") +
  labs(title="WILL THE TRAINING A WOMAN GETS IN THE WAC BE USEFUL IN CIVILIAN LIFE? ", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q20A. ARE MOST OF THE JOBS IN THE WAC INTERESTING AND AGREEABLE? 1. YES 2. NO 0. NO ANSWER
s195b$Q.20A. <- recode_factor(s195b$Q.20A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.20B. <- recode_factor(s195b$Q.20B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")


s195b %>%
  ggplot( aes(x=Q.20A., fill = Q.20B.)) +geom_bar(position= "fill") +
  labs(title="ARE MOST OF THE JOBS IN THE WAC INTERESTING AND AGREEABLE?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q21A. IS BEING A WAC BAD FOR A GIRL'S REPUTATION? 1. YES 2. NO 0. NO ANSWER
s195b$Q.21A. <- recode_factor(s195b$Q.21A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.21B. <- recode_factor(s195b$Q.21B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.21A., fill = Q.21B.)) +geom_bar(position= "fill") +
  labs(title="IS BEING A WAC BAD FOR A GIRL'S REPUTATION?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q22A. IS THE ARMY ANY PLACE FOR A GIRL TO BE? 1. YES 2. NO 0. NO ANSWER
s195b$Q.22A. <- recode_factor(s195b$Q.22A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.22B. <- recode_factor(s195b$Q.22B.,`1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.22A., fill = Q.22B.)) +geom_bar(position= "fill") +
  labs(title="IS THE ARMY ANY PLACE FOR A GIRL TO BE?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q23A. DO WAC OFFICERS DESERVE A SALUTE JUST THE SAME AS MEN OFFICERS? 1. YES 2. NO 0. NO ANSWER
s195b$Q.23A. <- recode_factor(s195b$Q.23A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.23B. <- recode_factor(s195b$Q.23B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.23A., fill = Q.23B.)) +geom_bar(position= "fill") +
  labs(title="DO WAC OFFICERS DESERVE A SALUTE JUST THE SAME AS MEN OFFICERS? ", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

# S195B.Q24A. DO WAC'S GET RATINGS A LOT EASIER THAN MEN? 1. YES 2. NO 0. NO ANSWER
s195b$Q.24A. <- recode_factor(s195b$Q.24A., `1` = "Yes", `2` = "No", `0` = "No Answer")
s195b$Q.24B. <- recode_factor(s195b$Q.24B., `1` = "Very Strongly", `2` = "Fairly Strongly", `3` = "Not Strongly", `0` = "No Answer")

s195b %>%
  ggplot( aes(x=Q.24A., fill = Q.24B.)) +geom_bar(position= "fill") +
  labs(title="DO WAC'S GET RATINGS A LOT EASIER THAN MEN?", x="Answers Level", y = "Proportion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = rev(my_cols[1:4]))

```
