---
title: "Spatial Arrangement in S32"
author: "Mary Solomon"
date: "7/19/2020"
output: html_document
---

An aspect of racial segregation that we want to analyze is segregation related to spatial arrangement. Spatial segregation of Black Americans was enforced in the American South with numerous local and state laws known as the Jim Crow laws from late 19th century to early 20th century. [include more context].

We are interested to see if themes of spatial segregation are prevelant in the soldiers' responses and experiences in the army during WWII.


```{r setup, include=FALSE}
#libraries
library(tidytext)
library(data.table)
library("RPostgreSQL")
library(stringi)
library(textstem)
library(dplyr)
library(tidyr)
library(SnowballC)
library(igraph)
library(ggraph)
library(widyr)
library(stringr)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
```

```{r functions, include = FALSE}
# Visualizing Bigrams functions
# From tidytext documentation
visualize_bigrams <- function(bigrams, title) {
  set.seed(2020)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void() + theme(legend.position = "none",
                      plot.title = element_text(hjust = 0.5)) +
    ggtitle(title)
}
```

```{r dataload, include=FALSE}
conn <- dbConnect(drv = PostgreSQL(),
                  dbname = "sdad",
                  host = "10.250.124.195",
                  port = 5432,
                  user = Sys.getenv("db_userid"),
                  password = Sys.getenv("db_pwd"))
# query the bipartite edgelist data from github data
data <- dbGetQuery(conn, "SELECT * FROM american_soldier.survey_32_clean")
dbDisconnect(conn)
```

```{r dictionaryload, include=FALSE}
#alterations to data
##### some data cleaning
#remove possessive 's
data$outfits_comment <- str_replace_all(data$outfits_comment, "'s", "")
data$long <- str_replace_all(data$long, "'s", "")

#stem and lem gender words as well
#load dictionary csv
spatial_words <- fread("~/git/dspg2020amsoldier/data/dictionary/spatial_arrangement.csv", sep = ",")
space_match <- paste(paste("\\b", spatial_words$space,"\\b", sep = ""), collapse="|") #regex friendly 

####collapse certain two word phrases like white man --> whiteman
#read the csv file of correct spellings back in.
collapse <- fread("~/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",") # (n=274)
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) #so that stringr doesn't pick up on instances where it is part of another word

#replace with collapsed words
data$long <- stri_replace_all_regex(data$long, collapse$original, collapse$collapse, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, collapse$collapse, vectorize_all = FALSE)

#### create custom stop words 
custom_stop <- append(stop_words$word, c("question", "questionnaire", "answer"))
```


```{r data_subset, include = FALSE}
#subset data based on question and race
S32W_short <- data %>% filter(racial_group== "white") %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32W_short <- tibble(nrow=1:nrow(S32W_short), text = S32W_short$outfits_comment)

S32W_long <- data %>% filter(racial_group== "white") %>% select(long) %>% filter(!is.na(long))
S32W_long <- tibble(nrow=1:nrow(S32W_long), text = S32W_long$long)

S32N_long <- data %>% filter(racial_group== "black") %>% select(long) %>% filter(!is.na(long))
S32N_long <- tibble(nrow=1:nrow(S32N_long), text = S32N_long$long)

```


```{r bigram_create, include = FALSE, echo = FALSE}
short_bigrams_space <- S32W_short %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(space_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>% 
  count(word1, word2, sort = TRUE)

longW_bigrams_space <- S32W_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(space_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>% 
  count(word1, word2, sort = TRUE)

longN_bigrams_space <- S32N_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(space_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE)

```



```{r bigram_visualize}
visualize_bigrams(short_bigrams_space, "White Soldiers' Outfits Response - Spatial Arrangement") 
visualize_bigrams(longW_bigrams_space, "White Soldiers' Long Response - Spatial Arrangement")
visualize_bigrams(longN_bigrams_space, "Black Soldiers' Long Response - Spatial Arrangement")
```

Some notable nodes in the white soldiers' response is south, train, camp, town and post. Bigrams for the word South include hate and dislike. The node town is most commonly followed by the word police.



### Co-occurences:
```{r}
cooccur_spatial <- function(data, n=5, corr=.15){
  #load dictionary csv
  spatial_words <- fread("~/git/dspg2020amsoldier/data/dictionary/spatial_arrangement.csv", sep = ",")
  space_match <- stem_words(lemmatize_words(spatial_words$space))
  space_match <- paste(paste("\\b", space_match,"\\b", sep = ""), collapse="|") #regex friendly 
  
  custom_stop <- append(stop_words$word, c("question", "questionnaire", "answer"))
  
  data %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% custom_stop) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= n) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(space_match, item1))%>%
  filter(correlation > corr) 
}

cooccur_spatial_edit <- function(data, n=5, corr=.15){
  #load dictionary csv
  spatial_words <- fread("~/git/dspg2020amsoldier/data/dictionary/spatial_arrangement_edit.csv", sep = ",")
  space_match <- stem_words(lemmatize_words(spatial_words$space))
  space_match <- paste(paste("\\b", space_match,"\\b", sep = ""), collapse="|") #regex friendly 
  
  custom_stop <- append(stop_words$word, c("question", "questionnaire", "answer"))
  
  data %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% custom_stop) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= n) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(space_match, item1))%>%
  filter(correlation > corr) 
}


visualize_cooccur <- function(data, title){
  set.seed(2020)
  data %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle(title)
}
```



white soldiers short response
```{r}
S32W_short_cors <- cooccur_spatial(S32W_short, n = 5, corr = 0.15) 

#plot
visualize_cooccur(S32W_short_cors, "White Soldiers' Short Response - Spatial Arrangement Co-occurences")
```



white soldiers long response
```{r}
S32W_long_cors <- cooccur_spatial(S32W_long) 

#plot
visualize_cooccur(S32W_long_cors, "White Soldiers' Long Response - Spatial Arrangement Co-occurences")
```


black soldiers long response
```{r}
S32N_long_cors <- cooccur_spatial(S32N_long) 

#plot
visualize_cooccur(S32N_long_cors, "Black Soldiers' Long Response - Spatial Arrangement Co-occurences")
```



#### Difference between white soldiers for segregation and those for integration
```{r}
segregation <- filter(data, outfits == "['They should be in separate outfits']")
integration  <- filter(data, outfits == "['They should be together in the same outfits']")
```

##### co-occurrences of the short response
```{r}
segregation_short <- segregation %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
seg_short <- tibble(nrow=1:nrow(segregation_short), text = segregation_short$outfits_comment)

integration_short <- integration %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
int_short <- tibble(nrow=1:nrow(integration_short), text = integration_short$outfits_comment)
```

```{r}
seg_short_cors <- cooccur_spatial(seg_short, n = 5, corr = 0.10) 

#plot
visualize_cooccur(seg_short_cors, "Pro Segregation Short Response - Spatial Arrangement Co-occurrences")
```



```{r}
int_short_cors <- cooccur_spatial(int_short, n = 0, corr = 0.10) 

#plot
visualize_cooccur(int_short_cors, "Pro Integration Short Response - Spatial Arrangement Co-occurrences")
```



Although these soldiers suported integration there is commentary about conditions in which the Black and White soldiers would share the same space. For the rightmost branch of cooccurrences,  example we see that both sleep and px were associated with separation. 

There is a burst/cluster surrounding the nodes Southern, Northern and live. When talking about possibly integrating outfits, the interactions of southerners and northerners were a significant topic. Perhaps soldiers are talking about the differences in culture between the southerners and northerners on regards to race relations. We also see that other ethnicities such as Chinese and Filipino are mentioned.


##### Co-occurances for long response

```{r}
segregation_long <- segregation %>% select(long) %>% filter(!is.na(long))
seg_long <- tibble(nrow=1:nrow(segregation_long), text = segregation_long$long)

integration_long <- integration %>% select(long) %>% filter(!is.na(long))
int_long <- tibble(nrow=1:nrow(integration_long), text = integration_long$long)
```

```{r}
### for segregation ####
seg_long_cors <- cooccur_spatial(seg_long, n = 5, corr = 0.15) 
#plot
visualize_cooccur(seg_long_cors, "Pro Segregation Long Response - Spatial Arrangement Co-occurrences")


### for integration ###
int_long_cors <- cooccur_spatial(int_long, n = 3, corr = 0.30) 
#plot
visualize_cooccur(int_long_cors, "Pro Integration Long Response - Spatial Arrangement Co-occurrences")
```





