---
title: "Topic Models"
author: "Saimun"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE, echo = F}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(data.table)
library(tidyr)
library(BTM)
library(udpipe)
library(networkD3)
library(plyr)
library(SnowballC)
library(tidytext)
library(topicmodels)

# require(devtools) 
# install_version("igraph", version = "1.2.4", repos = "http://cran.us.r-project.org")
library(igraph)
library(ggraph)
library(concaveman)
library(textplot)
library(stopwords)
library(dplyr)
```

```{r function, include = FALSE}
tidy_topic_probs = function(model){
  df <- cbind(source = rownames(model$phi), model$phi)
  rownames(df) <- 1:nrow(df)
  df = as.data.frame(df)
  edge_list = reshape2::melt(df, id.vars=c("source"), variable.name = "target", value.name = "weight")
}
```


```{r data, include = FALSE}
library("RPostgreSQL")
# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(),
                  dbname = "sdad",
                  host = "10.250.124.195",
                  port = 5432,
                  user = Sys.getenv("db_userid"),
                  password = Sys.getenv("db_pwd"))
# query the bipartite edgelist data from github data
data <- dbGetQuery(conn, "SELECT *
                   FROM american_soldier.survey_32_clean")
# disconnect from postgresql
dbDisconnect(conn)
S32N = data %>% filter(racial_group == "black")
S32W = data %>% filter(racial_group == "white")
```
```{r, include = FALSE}
biterms_n = read.csv(here::here("data","biterms_n.csv"))
biterms_77 = read.csv(here::here("data","biterms_77.csv"))
biterms_78 = read.csv(here::here("data","biterms_78.csv"))



traindata_n = read.csv(here::here("data","traindata_n.csv"))
traindata_77 = read.csv(here::here("data","traindata_77.csv"))
traindata_78 = read.csv(here::here("data","traindata_78.csv"))

row.names(traindata_n) <- traindata_n$X
row.names(traindata_77) <- traindata_77$X
row.names(traindata_78) <- traindata_78$X

```


```{r lda, include = FALSE}
text77_df <- tibble(row = 1:nrow(S32W), text = S32W$outfits_comment, outfits = S32W$outfits) #Written response to "should soldiers be in separate outfits?"
text78_df <- tibble(row = 1:nrow(S32W), text = S32W$long) #Written response on overall thoughts on the survey
textn_df <- tibble(row = 1:nrow(S32N), text = S32N$long) #Written response to "should soldiers be in separate outfits?"

# laod in stop words: words without any true meaning
data(stop_words)

# Bunch of useless one word responses
useless_responses = c("none","None","0", "12","none.","[none]","noone","[blank]","gujfujuj", "None.", "I", NA)

tidy_77 <- text77_df %>%
  filter(!text %in% useless_responses) %>% #filtering out useless 1 word responses
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  mutate(word = wordStem(word)) %>%
  group_by(row) %>%
  dplyr::count(word, sort = T) %>%
  mutate(response = "short", race = "white")

tidy_78 <- text78_df %>%
  filter(!text %in% useless_responses) %>% #filtering out useless 1 word responses
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  mutate(word = wordStem(word)) %>%
  group_by(row) %>%
  dplyr::count(word, sort = T) %>%
  mutate(response = "long", race = "white")

tidy_n <- textn_df %>%
  filter(!text %in% useless_responses) %>% #filtering out useless 1 word responses
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  mutate(word = wordStem(word)) %>%
  group_by(row) %>%
  dplyr::count(word, sort = T) %>%
  mutate(response = "long", race = "black")


# lda ---------------------------------------------------------------
# LDA finds topics depending on the number of clusters you want
# number of clusters we want

dtm_77 <- cast_dtm(tidy_77, term = word, document = row, value = n)
dtm_78 <- cast_dtm(tidy_78, term = word, document = row, value = n)
dtm_n <- cast_dtm(tidy_n, term = word, document = row, value = n)

num_clusters <- 6
weight_strength = .01
lda_77 <- LDA(dtm_77, k = num_clusters, method = "Gibbs", control = NULL)
lda_78 <- LDA(dtm_78, k = num_clusters, method = "Gibbs", control = NULL)
lda_n <- LDA(dtm_n, k = num_clusters, method = "Gibbs", control = NULL)

# this will separate out topics and have a weighted probability
topics_77_lda <- tidy(lda_77, matrix = "beta")
topics_78_lda <- tidy(lda_78, matrix = "beta")
topics_n_lda <- tidy(lda_n, matrix = "beta")

#takes word topic betas and graphs them as a network
colnames(topics_n_lda) = colnames(topics_77_lda) = colnames(topics_78_lda) =  c("source", "target", "weight")
```

## Topic Model Networks

A topic model put simply models the topics in a piece of text and the words that are associated with each topic. Naturally, words may fall in multiple topics and the model accounts for this by giving each topic a probability distribution over the words. A Topic Model Network is a useful way to visualize the topics and the words associated with each topic. Here we will explore two different topic models.

### Latent Dirichlet Allocation

Latent Dirchlet Allocation, or LDA, is the typical go to method for topic modelling. We chose to model the texts with 6 topics. We can see that in the three networks this produces very disconnected topics which intuitively seems to be a poor fit as the corpus is rather small and the soldiers are responding to direct and specific questions. LDA does produce a better connected network for the white soldiers outfits comment but does not do a great job in delineating the topics.

#### Black Soldiers Long Comment
```{r black lda, echo = F}
edgelist_n_lda= topics_n_lda %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- paste("Topic", edgelist_n_lda$source)
targets <- edgelist_n_lda$target
node_names <- factor(unique(c(sort(unique(sources)), as.character(targets))))



groups = edgelist_n_lda %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_n_lda$weight)
net_n_lda = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_n_lda
```

#### White Soldiers Outfits Comment
```{r 77 lda, echo = F}
edgelist_77_lda= topics_77_lda %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- paste("Topic", edgelist_77_lda$source)
targets <- edgelist_77_lda$target
node_names <- factor(unique(c(sort(unique(sources)), as.character(targets))))



groups = edgelist_77_lda %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_77_lda$weight)
net_77_lda = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_77_lda
```

#### White Soldiers Long Comment
```{r 78 lda, echo=F}
edgelist_78_lda= topics_78_lda %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- paste("Topic", edgelist_78_lda$source)
targets <- edgelist_78_lda$target
node_names <- factor(unique(c(sort(unique(sources)), as.character(targets))))



groups = edgelist_78_lda %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_78_lda$weight)
net_78_lda = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_78_lda
```

### BTM

There are some drawbacks to using LDA for our dataset, namely it doesn't handle short texts well. That is why we also implemented a [Biterm Topic Model](https://cran.r-project.org/web/packages/BTM/index.html) that does better on short texts. Overall, it seems that the topic model networks produced this way strike a better balance between effectively delineating the topics and showing interconnectivity. 
```{r btm, include = FALSE}

K = 6
modeln      <- BTM(traindata_n[-1], biterms = biterms_n[-1], k = K, iter = 2000, background = TRUE, trace = 100)
model77     <- BTM(traindata_77[-1], biterms = biterms_77[-1], k = K, iter = 2000, background = TRUE, trace = 100)
model78     <- BTM(traindata_78[-1], biterms = biterms_78[-1], k = K, iter = 2000, background = TRUE, trace = 100)
```
```{r, include = FALSE}
V = c("V2","V3", "V4", "V5", "V6", "V7", "V8", "V9", "V10")
topics = c("Topic 1","Topic 2", "Topic 3", "Topic 4", "Topic 5", "Topic 6", "Topic 7", "Topic 8", "Topic 9")

topics_n_btm = tidy_topic_probs(modeln)
topics_n_btm$weight = as.numeric(topics_n_btm$weight)
topics_n_btm$target = topics_n_btm$target %>%
  mapvalues(from = V, to = topics)
topics_n_btm = topics_n_btm[, c(2, 1, 3)]

topics_77_btm = tidy_topic_probs(model77)
topics_77_btm$weight = as.numeric(topics_77_btm$weight)
topics_77_btm$target = topics_77_btm$target %>%
  mapvalues(from = V, to = topics)
topics_77_btm = topics_77_btm[, c(2, 1, 3)]

topics_78_btm = tidy_topic_probs(model78)
topics_78_btm$weight = as.numeric(topics_78_btm$weight)
topics_78_btm$target = topics_78_btm$target %>%
  mapvalues(from = V, to = topics)
topics_78_btm = topics_78_btm[, c(2, 1, 3)]


colnames(topics_n_btm) = colnames(topics_77_btm) = colnames(topics_78_btm) =  c("source", "target", "weight")
```

#### Black Soldiers Long Comment
```{r black btm, echo = F}
edgelist_n_btm= topics_n_btm %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- edgelist_n_btm$source
targets <- edgelist_n_btm$target
node_names <- factor(unique(c(sort(unique(as.character(sources))), as.character(targets))))



groups = edgelist_n_btm %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_n_btm$weight)
net_n_btm = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_n_btm
```

#### White Soldiers Outfits Comment
```{r 77 btm, echo = F}
edgelist_77_btm= topics_77_btm %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- edgelist_77_btm$source
targets <- edgelist_77_btm$target
node_names <- factor(unique(c(sort(unique(as.character(sources))), as.character(targets))))



groups = edgelist_77_btm %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_77_btm$weight)
net_77_btm = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_77_btm
```

#### White Soldiers Long Comment
```{r 78 btm, echo = F}
edgelist_78_btm= topics_78_btm %>%
  filter(weight >= .01) %>%
  arrange(target)

sources <- edgelist_78_btm$source
targets <- edgelist_78_btm$target
node_names <- factor(unique(c(sort(unique(as.character(sources))), as.character(targets))))



groups = edgelist_78_btm %>% group_by(target) %>% top_n(1, weight)
groups = groups$source
nodes <- data.frame(name = node_names, group = c(1:num_clusters, groups), size = 8)
links <- data.frame(source = match(sources, node_names) - 1, 
                    target = match(targets, node_names) - 1, 
                    value = edgelist_78_btm$weight)
net_78_btm = forceNetwork(Links = links, Nodes = nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.9, zoom = T)
net_78_btm
```
