---
title: "Text-Network Analysis of White & Black Soldiers"
description: "This page provides sentiment of race relations from Survey 32."
tags: ["R", "sna", "race relations"]
weight: 1
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{css, echo=FALSE}
/* this chunnk of code centers all of the headings */
h1, h2, h3 {
  text-align: center;
}
```


```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = F, fig.width = 8, fig.height = 6)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) ;

library(stringi)
library(data.table)
library(tidyverse)
library(tidytext)
library(textstem)
library(readxl)
library(SnowballC)
library(rvest)
library(tm)
library(topicmodels)
library(tidyr)
library(textdata)
library(wordcloud)
library(RColorBrewer)
library(igraph)
library(ggraph)
library(widyr)
library(stringr)
library(networkD3)
library(RColorBrewer)
library(usmap) 
library(viridis)
library(ggplot2)
library(BTM)
library(udpipe)
library(networkD3)
library(topicmodels)
library(concaveman)
library(textplot)
library(stopwords)
library(dplyr)
# to install ggradar, run the line commented out below
#devtools::install_github("ricardo-bion/ggradar", dependencies = TRUE)
#library(ggradar)
library(tibble)
library(scales)
library(fmsb)
library(sentimentr)
library(syn)

data(stop_words)
colors <- c("#e57200", "#232d4b")
collapse <- fread("/sfs/qumulo/qhome/kb7hp/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",")
#collapse <- fread("~/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",")
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) #so that stringr doesn't pick up on instances where it is part of another word
#replace with collapsed words
source(here::here("src", "load_data.R"))
source(here::here("src", "sentiment_analysis.R"))
source(here::here("src", "word_selection.R"))

data$long <- stri_replace_all_regex(data$long, collapse$original, collapse$collapse_union, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, collapse$collapse_union, vectorize_all = FALSE)

S32N <- filter(data, racial_group == "black")
S32W <- filter(data, racial_group == "white")

text77_df <- tibble(row = 1:nrow(S32W), text = S32W$outfits_comment, outfits = S32W$outfits) #Written response to "should soldiers be in separate outfits?"
text78_df <- tibble(row = 1:nrow(S32W), text = S32W$long) #Written response on overall thoughts on the survey
textn_df <- tibble(row = 1:nrow(S32N), text = S32N$long)
```

# Social Network Analysis

## Gephi Networks
```{r sna, echo=FALSE, message=FALSE, warning=FALSE}

```

## Social Networks with Unionized Terminology
Something that is important to us is soldiers' dicussions of inner-outer groups of people. A way that we decided to look at that was by unionizing biterms. For example, a naive co-occurence with "black" may be "people" but we care about the dicussion of "black people" rather than just the identification of "people" as co-occurring with the word "black". To do this we complete several unionizations of biterms to create co-occurrence networks of dicussions of groups of people.

### Long Responses
We complete unionized term co-occurences and social networks using long response textual data. We separate our analysis by race and report co-occurences and co-occurence networks for both black and white soldiers.

```{r unions, echo = FALSE, message=FALSE, warning=FALSE}
row_n_words <- textn_df %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word= textstem::lemmatize_words(word)) %>%
  mutate(word= wordStem(word))

# count words co-occuring within sections
word_pairs_n <- row_n_words %>%
  pairwise_count(word, section, sort = TRUE)

word_cors_n <- row_n_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(correlation > .1)
# write.csv(word_cors_n, "clean_black_long_edge_occur.csv")
#visualizes correlation network
# word_cors_n %>%
#   simpleNetwork(fontSize = 12, zoom =T)

# colorman, whiteman, coloredsoldi, negrosoldi, whitesoldi
word_cors_n %>%
  filter(item1 %in% c("blackmal", "whitemal")) %>%
  group_by(item1) %>%
  filter(item2 != "blackmal") %>%
  filter(item2 != "whitemal") %>%
  filter(item2 != "negro") %>%
  filter(item2 != "white") %>%
  filter(item2 != "color") %>%
  filter(item2 != "south") %>%
  filter(item2 != "southern") %>%
  top_n(6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  mutate(item1 = reorder(item1, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity", fill = "#E57200") +
  xlab("Co-Occurring Word") +
  facet_wrap(~ item1, scales = "free") +
  ggtitle("Co-Occurences with Terms for Black Males and White Males \nfrom Black Soldiers' Long Responses") +
  coord_flip() +
  theme_minimal()

set.seed(2016)
word_cors_n %>%
  filter(correlation > .2) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = TRUE) +
  geom_node_point(color = "#E57200", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Co-Occurences of Words from Black Soldiers' Long \nResponses at the 15 percent Threshold") +
  theme_void()

# white long response
row_78_words <- text78_df %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word= textstem::lemmatize_words(word)) %>%
  mutate(word= wordStem(word))

word_pairs_78 <- row_78_words %>%
  pairwise_count(word, section, sort = TRUE)

word_cors_78 <- row_78_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(correlation > .1)
# write.csv(word_cors_78, "clean_white_long_edge_occur.csv")
#visualizes correlation network
# word_cors_78 %>%
#   simpleNetwork(fontSize = 12, zoom =T)

# whiteman,

word_cors_78 %>%
  filter(item1 %in% c("whitemal", "blackmal")) %>%
  group_by(item1) %>%
  filter(item2 != "blackmal") %>%
  filter(item2 != "whitemal") %>%
  filter(item2 != "negro") %>%
  filter(item2 != "white") %>%
  filter(item2 != "color") %>%
  filter(item2 != "south") %>%
  filter(item2 != "southern") %>%
  top_n(6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  mutate(item1 = reorder(item1, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity", fill = "#2C4F6B") +
  xlab("Co-Occurring Word") +
  facet_wrap(~ item1, scales = "free") +
  ggtitle("Co-Occurences with Terms for Black Males and White Males \nfrom White Soldiers' Long Responses") +
  coord_flip() +
  theme_minimal()

set.seed(2016)
word_cors_78 %>%
  filter(correlation > .2) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = TRUE) +
  geom_node_point(color = "#2C4F6B", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Co-Occurences of Words from White Soldiers' Long \nResponses at the 15 percent Threshold") +
  theme_void()
```

### Short Responses

We complete the same unionized-analysis above but using only short-response data from white soldiers. We are unable to get enough data to create plots for the two different groups of white soldiers: pro-segregation and anti-segregation. The following analysis reflects terms used in the entire group of white soldiers.

```{r short, echo = FALSE, message=FALSE, warning=FALSE}

# for v against -------------------------------------------
# white for seg (w4)

# row_w4_words <- text77_df %>%
#   filter(outfits == "['They should be in separate outfits']") %>%
#   mutate(section = row_number()) %>%
#   filter(section > 0) %>%
#   unnest_tokens(word, text) %>%
#   filter(!word %in% stop_words$word) %>%
#   mutate(word= textstem::lemmatize_words(word)) %>%
#   mutate(word= wordStem(word))
# 
# word_pairs_w4 <- row_w4_words %>%
#   pairwise_count(word, section, sort = TRUE)
# 
# word_cors_w4 <- row_w4_words %>%
#   group_by(word) %>%
#   filter(n() >= 20) %>%
#   pairwise_cor(word, section, sort = TRUE)  %>%
#   filter(correlation > 0)
# #visualizes correlation network
# # word_cors_w4 %>%
# #   simpleNetwork(fontSize = 12, zoom =T)
# 
# # whiteman, negrosoldi
# word_cors_w4 %>%
#   filter(item1 %in% c("whitemal", "blackmal")) %>%
#   group_by(item1) %>%
#   filter(item2 != "blackmal") %>%
#   filter(item2 != "whitemal") %>%
#   filter(item2 != "negro") %>%
#   filter(item2 != "white") %>%
#   filter(item2 != "color") %>%
#   filter(item2 != "south") %>%
#   filter(item2 != "southern") %>%
#   top_n(6) %>%
#   ungroup() %>%
#   mutate(item2 = reorder(item2, correlation)) %>%
#   mutate(item1 = reorder(item1, correlation)) %>%
#   ggplot(aes(item2, correlation)) +
#   geom_bar(stat = "identity", fill = "#0E879C") +
#   xlab("Co-Occurring Word") +
#   facet_wrap(~ item1, scales = "free") +
#   ggtitle("Co-Occurences with 'Negro' and 'White' from Pro-segregation White Soldier's Short Comments") +
#   coord_flip()  +
#   theme_minimal()
# 
# set.seed(2016)
# word_cors_w4 %>%
#   filter(correlation > .15) %>%
#   graph_from_data_frame() %>%
#   ggraph(layout = "fr") +
#   geom_edge_link(aes(edge_alpha = correlation), show.legend = TRUE) +
#   geom_node_point(color = "#2C4F6B", size = 5) +
#   geom_node_text(aes(label = name), repel = TRUE) +
#   ggtitle("Co-Occurences of Words from White Soldiers' Pro-Segregation \nShort Responses at the 15 percent Threshold") +
#   theme_void()
# 
# # white against segregation (wag)
# row_wag_words <- text77_df %>%
#   filter(outfits == "['They should be together in the same outfits']") %>%
#   mutate(section = row_number()) %>%
#   filter(section > 0) %>%
#   unnest_tokens(word, text) %>%
#   filter(!word %in% stop_words$word) %>%
#   mutate(word= textstem::lemmatize_words(word)) %>%
#   mutate(word= wordStem(word))
# 
# word_pairs_wag <- row_wag_words %>%
#   pairwise_count(word, section, sort = TRUE)
# 
# word_cors_wag <- row_wag_words %>%
#   group_by(word) %>%
#   filter(n() >= 5) %>%
#   pairwise_cor(word, section, sort = TRUE) %>%
#   filter(correlation > 0)
# #visualizes correlation network
# # word_cors_wag %>%
# #   simpleNetwork(fontSize = 12, zoom =T)
# 
# # there arent any combos
# 
# word_cors_wag %>%
#   filter(item1 %in% c("whitemal", "blackmal")) %>%
#   group_by(item1) %>%
#   # filter(item2 != "blackmal") %>%
#   # filter(item2 != "whitemal") %>%
#   # filter(item2 != "negro") %>%
#   # filter(item2 != "white") %>%
#   # filter(item2 != "color") %>%
#   # filter(item2 != "south") %>%
#   # filter(item2 != "southern") %>%
#   top_n(6) %>%
#   ungroup() %>%
#   mutate(item2 = reorder(item2, correlation)) %>%
#   mutate(item1 = reorder(item1, correlation)) %>%
#   ggplot(aes(item2, correlation)) +
#   geom_bar(stat = "identity", fill = "#E6CE3A") +
#   xlab("Co-Occurring Word") +
#   facet_wrap(~ item1, scales = "free") +
#   ggtitle("Co-Occurences with 'Negro' and 'White' from Anti-segregation White Soldier's Short Comments") +
#   coord_flip()  +
#   theme_minimal()
# 
# set.seed(2016)
# word_cors_wag %>%
#   filter(correlation > .15) %>%
#   graph_from_data_frame() %>%
#   ggraph(layout = "fr") +
#   geom_edge_link(aes(edge_alpha = correlation), show.legend = TRUE) +
#   geom_node_point(color = "#E57200", size = 5) +
#   geom_node_text(aes(label = name), repel = TRUE) +
#   ggtitle("Co-Occurences of Words from Anti-Segregation White Soldiers' Short Responses at the 15 percent Threshold") +
#   theme_void()

row_77_words <- text77_df %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word= textstem::lemmatize_words(word)) %>%
  mutate(word= wordStem(word))

word_pairs_77 <- row_77_words %>%
  pairwise_count(word, section, sort = TRUE)

word_cors_77 <- row_77_words %>%
  group_by(word) %>%
  filter(n() >= 5) %>%
  pairwise_cor(word, section, sort = TRUE)
# write.csv(word_cors_77, "clean_white_short_occur.csv")
#visualizes correlation network
# word_cors_77 %>%
#   simpleNetwork(fontSize = 12, zoom =T)

word_cors_77 %>%
  filter(item1 %in% c("blackmal", "whitemal")) %>%
  group_by(item1) %>%
  filter(item2 != "blackmal") %>%
  filter(item2 != "whitemal") %>%
  filter(item2 != "negro") %>%
  filter(item2 != "white") %>%
  filter(item2 != "color") %>%
  filter(item2 != "south") %>%
  filter(item2 != "southern") %>%
  top_n(6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  mutate(item1 = reorder(item1, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity", fill = "#E6CE3A") +
  xlab("Co-Occurring Word") +
  facet_wrap(~ item1, scales = "free") +
  ggtitle("Co-Occurences with 'Negro' and 'White' from White Soldier's Short Comments") +
  coord_flip()  +
  theme_minimal()

set.seed(2016)
word_cors_77 %>%
  filter(correlation > .15) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = TRUE) +
  geom_node_point(color = "#E6CE3A", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Co-Occurences of Words from White Soldiers' Short \nResponses at the 15 percent Threshold") +
  theme_void()
```
